Autonomous Oceanographic Data Collection towards Estimating Excursion Sets of Vector-valued Random Fields

### 2020-06-12 main_new.tex
Updates from Overleaf

Monitoring the world's oceans has gained increased importance in light of the changing climate and increasing anthropogenic impact. 
\begin{comment} % TO BE RE-INSERTED LATER IN THE TEXT?
A central problem for understanding these factors is the lack of representative data with sufficient resolution. Most of this \emph{undersampling} can be attributed to the large spatio-temporal variations in which ocean processes transpire, prompting the need for effective means of sampling. By \emph{sampling}, we refer to the design of observational strategies in the spatial domain, where the use autonomous robotic platforms can be combined with statistical methods to pursue measurements with high scientific relevance. This combination, of statistical tools and robotic platforms, constitute a methodological basis for addressing the problem of efficient sampling of the ocean, which is at the core of this work.
\end{comment}
Central to understanding the changes taking place in the upper
water-column is knowledge of the bio-geophysical interaction driven by
an agglomeration of physical forcings (e.g. wind, topography,
bathymetry, tidal influences, etc.) and incipient micro-biology driven
by planktonic and coastal anthropogenic input, such as pollution and
agricultural runoff transported into the ocean by rivers and streams.
These often result in a range of ecosystem-related phenomena such as
blooms and plumes, with direct and indirect effects on society. \kc{we
  should look for a citation here. Check with John Ryan}
 One of the bottlenecks in the study of such phenomena lies however in the lack of obervational data with sufficient resolution. Most of this \emph{undersampling} can be attributed to the large spatio-temporal variations in which ocean processes transpire, prompting the need for effective means of data collection. 
%
 \textcolor{blue}{By \emph{sampling}, we refer here primarily to the design of observational strategies in the spatial domain %where the use autonomous robotic platforms can be combined with statistical methods 
 with the aim to pursue measurements with high scientific relevance}.
Based on collected data and sometimes also of prior knowledge, models from spatial statistics can be used to make predictions of the state variables under consideration over regions of interest. In case of multiple continuous state variables being jointly studied relying on spatially scattered data, vector-valued random field models and associated prediction approaches such as co-Kriging \citep[See, e.g.,][]{Wackernagel2003} can be considered nowadays as part of the standard statistical toolkit in oceanographic research and beyond. %applications and beyond.  
 %By \emph{sampling}, we refer to the design of observational strategies in the spatial domain, where the use autonomous robotic platforms can be combined with statistical methods to pursue measurements with high scientific relevance. This combination, of statistical tools and robotic platforms, constitute a methodological basis for addressing the problem of efficient sampling of the ocean, which is at the core of this work.

@@

The work presented here is primarily inspired by a case study 
%application where an AUV is used to measure both temperature and salinity in 
pertaining to the spatial characterization of a frontal system generated by
river plumes. Fig. \ref{fig:nidelven} shows the survey area in
Trondheim, Norway, where cold freshwater enters from the river,
creating a strong gradient in both temperature and salinity. Because
of the local topography and the Coriolis force the cold fresh water
tends to flow to the east. Depending on the river discharge, tidal
effects, wind, and temperature differences, this boundary often gets
distorted. Initial knowledge about the location and evolution of these
features are highly uncertain, making deterministic planning
challenging. Here the goal is to use AUV measurements towards a better identification of freshwater versus oceanic water, with the help of a vector-valued random field model for both temperature and salinity. As we will present in the next sections, some of the original contributions inspired by this specific problem are actually applicable to further settings and application areas. \\

@@

\section{Quantifying uncertainty on Excursion Sets implicitly defined by Gaussian processes}
\label{sec:ESEP}

@@

%In the end, this result is integrated over the spatial domain $x \in X$.

>>>>

Monitoring the world's oceans has gained increased importance in light of the changing climate and increasing anthropogenic impact. 
\begin{comment} % TO BE RE-INSERTED LATER IN THE TEXT?
A central problem for understanding these factors is the lack of representative data with sufficient resolution. Most of this \emph{undersampling} can be attributed to the large spatio-temporal variations in which ocean processes transpire, prompting the need for effective means of sampling. By \emph{sampling}, we refer to the design of observational strategies in the spatial domain, where the use autonomous robotic platforms can be combined with statistical methods to pursue measurements with high scientific relevance. This combination, of statistical tools and robotic platforms, constitute a methodological basis for addressing the problem of efficient sampling of the ocean, which is at the core of this work.
\end{comment}
Central to understanding the changes taking place in the upper
water-column is knowledge of the bio-geophysical interaction driven by
an agglomeration of physical forcings (e.g. wind, topography,
bathymetry, tidal influences, etc.) and incipient micro-biology driven
by planktonic and coastal anthropogenic input, such as pollution and
agricultural runoff transported into the ocean by rivers and streams.
These often result in a range of ecosystem-related phenomena such as
blooms and plumes, with direct and indirect effects on society. \kc{we
  should look for a citation here. Check with John Ryan}
 One of the bottlenecks in the study of such phenomena lies however in the lack of observational data with sufficient resolution. Most of this \emph{undersampling} can be attributed to the large spatio-temporal variations in which ocean processes transpire, prompting the need for effective means of data collection. 
%
 \textcolor{blue}{By \emph{sampling}, we refer here primarily to the design of observational strategies in the spatial domain %where the use autonomous robotic platforms can be combined with statistical methods 
 with the aim to pursue measurements with high scientific relevance}.
Based on collected data and sometimes also of prior knowledge, models from spatial statistics can be used to make predictions of the state variables under consideration over regions of interest. In case of multiple continuous state variables being jointly studied relying on spatially scattered data, vector-valued random field models and associated prediction approaches such as co-Kriging \citep[See, e.g.,][]{Wackernagel2003} can be considered nowadays as part of the standard statistical toolkit in oceanographic research and beyond. %applications and beyond.  
 %By \emph{sampling}, we refer to the design of observational strategies in the spatial domain, where the use autonomous robotic platforms can be combined with statistical methods to pursue measurements with high scientific relevance. This combination, of statistical tools and robotic platforms, constitute a methodological basis for addressing the problem of efficient sampling of the ocean, which is at the core of this work.

@@

The work presented here is primarily inspired by a case study 
%application where an AUV is used to measure both temperature and salinity in 
pertaining to the spatial characterization of a frontal system generated by
river plumes. Fig. \ref{fig:nidelven} shows the survey area in
Trondheim, Norway, where cold freshwater enters from the river,
creating a strong gradient in both temperature and salinity. Because
of the local topography and the Coriolis force the cold fresh water
tends to flow to the east. Depending on the river discharge, tidal
effects, wind, and temperature differences, this boundary often gets
distorted. Initial knowledge about the location and evolution of these
features are highly uncertain, making deterministic planning
challenging. Here the goal is to use AUV measurements towards a better description of the interface between freshwater versus oceanic water, with the help of a vector-valued random field model for both temperature and salinity. As we will present in the next sections, some of the original contributions inspired by this specific problem are actually applicable to further settings and application areas. \\

@@

\input{section2}

\begin{comment}
\section{Quantifying uncertainty on Excursion Sets implicitly defined by Gaussian processes}
\label{sec:ESEP}

@@

%In the end, this result is integrated over the spatial domain $x \in X$.
\end{comment}
